### 2018-04-30 doc/paper.tex
Adding the error plot to the main document.
Removing the references that are actually used from "bogus" section.
Adding the original JLCS10 plot to introduction.
Also

- Changing `linkcolor` to `MidnightBlue` (the default `red`
  was too foreboding)
- Changing from `darkgrid` to `white` theme for the plots
  (this results in a lot less going on)
- Adding `de_casteljau.jlcs10_compensated` as a distinct
  implementation. The key difference being the order of operations
  in computing `r b1 + s b2 + l_hat`.
- Updating section labels from `{foo}` to `{sec:foo}`

\usepackage[usenames, dvipsnames]{color}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  citecolor=ForestGreen,
  pdfinfo={
    CreationDate={D:20180425160342},
    ModDate={D:20180425160342},
  },
}

@@

To address ill-conditioned problems, error-free transformations (EFT) can
be applied in \textit{compensated algorithms} to account for roundoff.
Error-free transformations were studied in great detail in \cite{Ogita2005}
and open a large number of applications.
In \cite{langlois_et_al:DSP:2006:442}, a compensated Horner's algorithm was
described to evaluate a polynomial in the monomial basis. In \cite{Jiang2010},
a similar method was described to perform a compensated version of the de
Casteljau algorithm. In both cases, the \(\cond{p, s}\) factor is moved
from \(\mach\) to \(\mach^2\) and the computed value is as accurate
as if the computations were done in twice the working precision. For example,
the compensated de Casteljau algorithm (\texttt{CompDeCasteljau}) satisfies
\begin{equation}\label{de-casteljau-2-error}
  \frac{\left|p(s) - \mathtt{CompDeCasteljau}(p, s)\right|}{
    \left|p(s)\right|} \leq \mach + \cond{p, s} \times
    \mathcal{O}\left(\mach^2\right).
\end{equation}
For problems with \(\cond{p, s} < 1 / \mach^2\), the relative error
is \(\mach\), i.e. accurate to full precision, aside from rounding to the
nearest floating point number.

@@

As in~\eqref{de-casteljau-error}, the accuracy of the compensated
result~\eqref{de-casteljau-2-error} may be arbitrarily bad for ill-conditioned
polynomial evaluations. We describe how to defer rounding into progressively
smaller error groups and improve the accuracy of the computed result by a
factor of \(\mach\) for every error group added. So we derive
\texttt{CompDeCasteljauK}, a \(K\)-fold compensated de Casteljau algorithm
that satisfies the following a prior bound for any arbitrary integer \(K\):
\begin{equation}
  \frac{\left|p(s) - \mathtt{CompDeCasteljauK}(p, s)\right|}{
    \left|p(s)\right|} \leq \mach + \cond{p, s} \times
    \mathcal{O}\left(\mach^K\right).
\end{equation}
This means that the computed value with \texttt{CompDeCasteljauK} is now
as accurate as the result of the de Casteljau algorithm performed in
\(K\) times the working precision with a final rounding back to this
working precision.

The paper is organized as follows. Section~\ref{notation} introduces some
basic notation and results about floating point arithmetic, error-free
transformations and the de Casteljau algorithm. In Section~\ref{compensated-2},
the compensated algorithm for polynomial evaluation from \cite{Jiang2010} is
reviewed and notation is established for the expansion. In
Section~\ref{compensated-k}, the \(K\) compensated algorithm is provided and
a forward error analysis is performed. Finally, in Section~\ref{numerical} we
give numerical tests to illustrate the practical efficiency of our algorithms.

\section{Basic notation and results}\label{notation}

@@

\section{Compensated de Casteljau}\label{compensated-2}

@@

\section{\texorpdfstring{\(K\)}{K} Compensated de Casteljau}\label{compensated-k}

@@

\section{Numerical experiments}\label{numerical}

Placeholder

@@

Here they are, for now
\begin{itemize}
  \item Compensated Horner (\(K = 2\)) (\cite{langlois_et_al:DSP:2006:442})
  \item Compensated de Casteljau (\cite{Jiang2010})
  \item Newton with compensated Horner (\cite{Graillat2008})
  \item \(K\)-fold Sum (\cite{Ogita2005})
  \item \(K\)-fold Horner (\cite{Graillat2009})
\end{itemize}

>>>>

\usepackage[usenames, dvipsnames]{color}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=MidnightBlue,
  citecolor=ForestGreen,
  pdfinfo={
    CreationDate={D:20180425160342},
    ModDate={D:20180425160342},
  },
}

@@

To address ill-conditioned problems, error-free transformations (EFT) can
be applied in \textit{compensated algorithms} to account for roundoff.
Error-free transformations were studied in great detail in \cite{Ogita2005}
and open a large number of applications.
In \cite{langlois_et_al:DSP:2006:442}, a compensated Horner's algorithm was
described to evaluate a polynomial in the monomial basis. In \cite{Jiang2010},
a similar method was described to perform a compensated version of the de
Casteljau algorithm. In both cases, the \(\cond{p, s}\) factor is moved
from \(\mach\) to \(\mach^2\) and the computed value is as accurate
as if the computations were done in twice the working precision. For example,
the compensated de Casteljau algorithm (\texttt{CompDeCasteljau}) satisfies
\begin{equation}\label{de-casteljau-2-error}
  \frac{\left|p(s) - \mathtt{CompDeCasteljau}(p, s)\right|}{
    \left|p(s)\right|} \leq \mach + \cond{p, s} \times
    \mathcal{O}\left(\mach^2\right).
\end{equation}
For problems with \(\cond{p, s} < 1 / \mach^2\), the relative error
is \(\mach\), i.e. accurate to full precision, aside from rounding to the
nearest floating point number. Figure~\ref{fig:jlcs-10} shows this shift
in relative error from \texttt{DeCasteljau} to \texttt{CompDeCasteljau}.

\begin{figure}
  \includegraphics[width=0.8125\textwidth]{../images/jlcs10_plot.pdf}
  \centering
  \caption{Evaluation of \(p(s) = (s - 1)\left(s - 3/4\right)^7\)
    represented in Bernstein form.}
  \label{fig:jlcs-10}
\end{figure}

@@

As in~\eqref{de-casteljau-error}, the accuracy of the compensated
result~\eqref{de-casteljau-2-error} may be arbitrarily bad for ill-conditioned
polynomial evaluations. For example, as the condition number grows in
Figure~\ref{fig:jlcs-10}, some points have relative error exactly equal to
\(1\); this indicates that \(\mathtt{CompDeCasteljau}(p, s) = 0\), which is
a complete failure to evaluate the order of magnitude of \(p(s)\).
We describe how to defer rounding into progressively
smaller error groups and improve the accuracy of the computed result by a
factor of \(\mach\) for every error group added. So we derive
\texttt{CompDeCasteljauK}, a \(K\)-fold compensated de Casteljau algorithm
that satisfies the following a prior bound for any arbitrary integer \(K\):
\begin{equation}
  \frac{\left|p(s) - \mathtt{CompDeCasteljauK}(p, s)\right|}{
    \left|p(s)\right|} \leq \mach + \cond{p, s} \times
    \mathcal{O}\left(\mach^K\right).
\end{equation}
This means that the computed value with \texttt{CompDeCasteljauK} is now
as accurate as the result of the de Casteljau algorithm performed in
\(K\) times the working precision with a final rounding back to this
working precision.

The paper is organized as follows. Section~\ref{sec:notation} introduces some
basic notation and results about floating point arithmetic, error-free
transformations and the de Casteljau algorithm. In
Section~\ref{sec:compensated-2},
the compensated algorithm for polynomial evaluation from \cite{Jiang2010} is
reviewed and notation is established for the expansion. In
Section~\ref{sec:compensated-k}, the \(K\) compensated algorithm is provided and
a forward error analysis is performed. Finally, in Section~\ref{sec:numerical} we
give numerical tests to illustrate the practical efficiency of our algorithms.

\section{Basic notation and results}\label{sec:notation}

@@

\section{Compensated de Casteljau}\label{sec:compensated-2}

@@

\section{\texorpdfstring{\(K\)}{K} Compensated de Casteljau}\label{sec:compensated-k}

@@

\section{Numerical experiments}\label{sec:numerical}

\begin{figure}[H]
  \includegraphics[width=0.8125\textwidth]{../images/de_casteljau_rel_error.pdf}
  \centering
  \caption{Accuracy of evaluation of \(p(s) = (s - 1)\left(s - 3/4\right)^7\)
    represented in Bernstein form.}
\end{figure}

@@

Here they are, for now
\begin{itemize}
  \item Newton with compensated Horner (\cite{Graillat2008})
\end{itemize}
